Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-02-04 Paper/Manuscript.tex
Moved the tau eff description

The generated signal $\ytxe(\timesym)$ is converted to an analogue electric signal and amplified by the transceiver to obtain analogue signal $\ytxe(\timesym)$. The analogue and amplified signal is passed on to the transducer to generate the transmitted acoustic signal $\ytxA(\timesym)$ in the water column, where $\timesym$ is the time for the (analog) signal. For a split-aperture echosounder system, there are typically three or four channels to allow estimation of the angle of arriving echoes, and the signal is typically transmitted with equal power across the channels.

@@

The auto correlation function of the matched filter signal, $\ymfauto(\samplesymt)$, that will be used in a later processing step is defined as:
\begin{equation}
\label{eq:TXAuto}
\ymfauto(\samplesymt) = \frac{\ymf(\samplesymt)*\ymf^*(-\samplesymt)}{||\ymf||^2_2}.
\end{equation}

\begin{figure}
\includegraphics{Fig_ACF}
\caption{\label{fi:ACF}.}
\end{figure}

@@

Volume backscattering samples compressed over the operational frequency band are estimated by applying Eq. \ref{eq:sv_f} to the received digitized power samples using the on-axis gain value with $f$ set to the centre frequency of the broadband pulse, $\fc$:
\begin{equation}
\label{eq:Sv}
\sv(\samplesymt)  =  10\log_{10}(\prxe(\samplesymt)) + 20\log_{10}(\range(\samplesymt)) + 2\absorp(\fc)\range(\samplesymt) 
- 10\log_{10}\left( \frac{\ptxe \wlen^2(\fc) \cw \teff \eqang(\fc) \gainzero^2(\fc)}{32\pi^2} \right),
\end{equation}
noting that $\sv(\samplesymt)$ is an average over frequency of all echoes received at sample $\samplesymt$. In this case, the time window, $\tslide$, is the effective pulse duration, $\teff$, resulting from pulse compression. The effective pulse duration is defined as the pulse duration at transmit power $\ptxe$ which produces the same energy as the actual transmitted pulse, and is estimated from digitized data via:
%
\begin{eqnarray}
\label{eq:TauEff}
\ptxauto(\samplesymt) & = & |\ymfauto(\samplesymt)|^2,\\
\teff & = & \frac{\sum \ptxauto(\samplesymt)}{\textrm{max}(\ptxauto(\samplesymt))\fsdec},
\end{eqnarray}
where $\ptxauto$ is the square of the absolute value of the matched filter autocorrelation function, and the summation is calculated over a duration of twice the nominal pulse duration, $2\tnom$. For an ideal system, i.e., no tapering at the rising and trailing edges of the transmitted signal, the effective pulse duration is the same as the transmit pulse duration.

>>>>

The generated signal $\ytxe(\timesym)$ is converted to an analogue electric signal and amplified by the transceiver to obtain analogue signal $\ytxe(\timesym)$. The analogue and amplified signal is passed on to the transducer to generate the transmitted acoustic signal $\ytxa(\timesym)$ in the water column, where $\timesym$ is the time for the (analog) signal. For a split-aperture echosounder system, there are typically three or four channels to allow estimation of the angle of arriving echoes, and the signal is typically transmitted with equal power across the channels.

@@

The auto correlation function of the matched filter signal and the effective pulse duration, defined as the pulse duration at transmit power $\ptxe$ which produces the same energy as the actual transmitted pulse, will be used in later processing steps and are defined as
\begin{equation}
\label{eq:TXAuto}
\ymfauto(\samplesymt) = \frac{\ymf(\samplesymt)*\ymf^*(-\samplesymt)}{||\ymf||^2_2}
\end{equation}
and
\begin{equation}
\label{eq:TauEff}
\teff = \frac{\sum \ptxauto(\samplesymt)}{\textrm{max}(\ptxauto(\samplesymt))\fsdec},
\end{equation}
where
\begin{equation*}
%\label{eq:TauEff}
\ptxauto(\samplesymt)  =  |\ymfauto(\samplesymt)|^2
\end{equation*}
is the square of the absolute value of the matched filter autocorrelation function, and the summation is calculated over a duration of twice the nominal pulse duration, $2\tnom$. For an ideal system, i.e., no tapering at the rising and trailing edges of the transmitted signal, the effective pulse duration is the same as the transmit pulse duration.

\begin{figure}
\includegraphics{Fig_ACF}
\caption{The aoutocorrekation function $\ptxauto$ from the example. The corresponding $\teff=0.1ms$ and $\tnom=2ms$\label{fi:ACF}.}
\end{figure}

@@

Volume backscattering samples compressed over the operational frequency band are estimated by applying Eq. \ref{eq:sv_f} to the received digitized power samples using the on-axis gain value with $f$ set to the centre frequency of the broadband pulse, $\fc$:
\begin{equation}
\label{eq:Sv}
\sv(\samplesymt)  =  10\log_{10}(\prxe(\samplesymt)) + 20\log_{10}(\range(\samplesymt)) + 2\absorp(\fc)\range(\samplesymt) 
- 10\log_{10}\left( \frac{\ptxe \wlen^2(\fc) \cw \teff \eqang(\fc) \gainzero^2(\fc)}{32\pi^2} \right),
\end{equation}
noting that $\sv(\samplesymt)$ is an average over frequency of all echoes received at sample $\samplesymt$. In this case, the time window, $\tslide$, is the effective pulse duration, $\teff$, resulting from pulse compression.
